Lessons Learned for JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors

### 2019-10-17 ms.tex
showing the Lakeshore T-change test

\clearpage
\subsection{FPA temperature change}
We purposely adjusted the focal plane array temperature set point mid-way through a long exposure to test how the detectors' temperatures will affect their response to light.
As can be seen in Figure \ref{fig:indTSeriesAfterLamp} (bottom panel) the Lakeshore temperature controlling a baseplate where the largest thermal mass sits is constant to within 3 mK.
The FPA temperature is adjusted upward by 300 mK about 75 minutes into the test and held at this higher value.
The change in temperature results in a 0.1\% increase in flux (ie. 1000 ppm).
In terms of slopes, this resulted in a change of 2.3 DN/s/px for detector 487 and 3.6 DN/s/px for detector 489.
For the integration times of 10.77 seconds, this amounts to 25 to 39 DN accumulated within an integration.
This is lower than the value of 80 DN for a 100 mK change in \citet{hall2005jwstArrays}, likely because it is calculated over the slope of an image rather than the absolute counts.

@@

>>>>

\clearpage
\subsection{Temperature Changes}
\subsubsection{FPA temperature change}
We purposely adjusted the focal plane array temperature set point mid-way through a long exposure to test how the detectors' temperatures will affect their response to light.
As can be seen in Figure \ref{fig:indTSeriesAfterLamp} (bottom panel) the Lakeshore temperature controlling a baseplate where the largest thermal mass sits is constant to within 3 mK.
The FPA temperature is adjusted upward by 300 mK about 75 minutes into the test and held at this higher value.
The change in temperature results in a 0.1\% increase in flux (ie. 1000 ppm).
In terms of slopes, this resulted in a change of 2.3 DN/s/px for detector 487 and 3.6 DN/s/px for detector 489.
For the integration times of 10.77 seconds, this amounts to 25 to 39 DN accumulated within an integration.
This is lower than the value of 80 DN for a 100 mK change in \citet{hall2005jwstArrays}, likely because it is calculated over the slope of an image rather than the absolute counts.

@@

\subsubsection{Lakeshore Temperature Change}

\begin{figure*}
{\gridline{\fig{individual_azlab06_sub320_lakeshore_to_39p7.pdf}{0.99\textwidth}{}}}
\caption{Time series during an adjustment to the Lakeshore set point.}\label{fig:indTSeriesLakeshore39p7}
\end{figure*}
